---
title: "ACM Ass3 experimentation"
author: "Manon Grandjean"
date: "2023-04-20"
output: html_document
---

```{r}
library(extraDistr)
library(tidyverse)
library(brms)
```

Parameters:
*Bias* is a persons tendency towards being more trusting or less trusting overall (on the first rating)
*precision1* is how much we vary around our bias when picking a first rating
*precision2* is the noise term when picking a second rating
*w1* is how much we trust our first rating
*w2* is how much we trust the other's rating

Observables:
*First rating* drawn from a beta distribution with a mean of bias (and a precision of precision1)
*Other rating* is randomly generated at either -3,-2,0,2,3 higher/lower than first rating. Equally likely (though still within 1-8)
*feedback* is difference between first and other rating
*Second rating* is drawn from a beta distribution with precision2 and a mean which is calculated as the inverse logit of a weighting our first and other ratings with their resepctive weights (ratings in log odds space) = logit_scaled(first rating) w1 + logit_scaled(other's rating) * w2


```{r Simple Bayes Agent function (1 trial)}
# create function that takes agent's parameters
SimAgent_SimpleBayes <- function(AgentID, bias, precision1, precision2){
  # generate a first rating (using bias and fixed sd) (between 0-1, so we have to transform to 1-8 afterwards)
  first <- round(rprop(1, mean = bias, size = precision1)*7+1)
          #size is a precision parameters (2 = uniform)
          # "*7+1" transform from 0-1 space to 1-8 space :-)
  
  # generate other rating and calculate feedback
  feedback <- sample(c(-3,-2,0,2,3), size = 1)
  other <- first+feedback
  
  while(other < 1 | other > 8){
    feedback <- sample(c(-3,-2,0,2,3), size = 1)
    other <- first+feedback
  }
  
  # generate second rating (using social conformity, first rating, and feedback)
  #second <- round(first + socialConf * feedback)
  # use log odds space
  second <- round(rprop(1,
                        mean = logit_scaled(first)*0.5 + logit_scaled(other)*0.5,
                        size = precision2))
  
  # save info to df
  #return(c(first,other,second))
  df <- data.frame(AgentID = AgentID,
                     FirstRating = first,
                     OtherRating = other,
                     Feedback = feedback,
                     SecondRating = second)
  return(df)
}


# see what precision we want
#hist(rprop(10000, mean = 0.6, size = 2))

```


```{r simulations dataframe}
# create empty df
simulationsSB <- data.frame(AgentID = c(),
                     FirstRating = c(),
                     OtherRating = c(),
                     Feedback = c(),
                     SecondRating = c())
```


```{r}
# make one agent per unique combinations 
agentsSB <- expand.grid(bias = seq(from = 0.1, to = 0.9, by = 0.1), # bias of 0 and of 1 give NA in rprop function!! 
                        precision1 = seq(from = 2, to = 100, by = 10),
                        precision1 = seq(from = 2, to = 100, by = 10)) 
                          # socialConf can only be negative if we allow contrarian agents
# Adding Agent IDs
agentsSB <- mutate(agentsSB, AgentID = paste0("ID_",row_number()))
```


```{r simulate ratings for all agents}

# number of trials per agent
trials = 2

for(i in 1:nrow(df_agents)){ # iterate over agents
  for(t in 1:trials){ # iterate over trials
    df_sim <- rbind(df_sim, SocialConformityAgent(df_agents$AgentID[i], df_agents$bias[i], df_agents$socialConf[i]))
  }
}

```




