---
title: "ACM Ass3 experimentation"
author: "Manon Grandjean"
date: "2023-04-20"
output: html_document
---

```{r}
library(extraDistr)
library(tidyverse)
```

Parameters:
*Social conformity* is how much a person adopts the other rating in their second rating
*Bias* is a persons tendency towards being more trusting or less trusting overall

Observables:
*First rating* drawn from a beta distribution with a mean of bias (and a fixed SD)
*Other rating* is randomly generated at either -3,-2,0,2,3 higher/lower than first rating. Equally likely (though still within 1-8)
*feedback* is difference between first and other rating
*Second rating* is = first rating + social conformity * feedback


```{r Agent function (1 trial)}
# create function that takes agent's parameters
SocialConformityAgent <- function(AgentID, bias, socialConf){
  # generate a first rating (using bias and fixed sd) (between 0-1, so we have to transform to 1-8 afterwards)
  first <- round(rprop(1, mean = bias, size = 3)*7+1)
          #size is a precision parameters (2 = uniform)
          # "*7+1" transform from 0-1 space to 1-8 space :-)
  
  # generate other rating and calculate feedback
  feedback <- sample(c(-3,-2,0,2,3), size = 1)
  other <- first+feedback
  
  while(other < 1 | other > 8){
    feedback <- sample(c(-3,-2,0,2,3), size = 1)
    other <- first+feedback
  }
  
  # generate second rating (using social conformity, first rating, and feedback)
  second <- round(first + socialConf * feedback)
  
  # save info to df
  #return(c(first,other,second))
  df <- data.frame(AgentID = AgentID,
                     FirstRating = first,
                     OtherRating = other,
                     Feedback = feedback,
                     SecondRating = second)
  return(df)
}


# see what precision we want
#hist(rprop(10000, mean = 0.5, size = 3))

```


```{r simulations dataframe}
# create empty df
df_sim <- data.frame(AgentID = c(),
                     FirstRating = c(),
                     OtherRating = c(),
                     Feedback = c(),
                     SecondRating = c())
```


```{r}
# make one agent per unique combinations 
df_agents <- expand.grid(bias = seq(from = 0.0, to = 1.0, by = 0.1),
                         socialConf = seq(from = 0.0, to = 1.0, by = 0.1)) 
                          # socialConf can only be negative if we allow contrarian agents
# Adding Agent IDs
df_agents <- mutate(df_agents, AgentID = paste0("ID_",row_number()))
```


```{r}
#df_sim <- rbind(df_sim,SocialConformityAgent("ID1", 0.5, 0.2))

# number of trials per agent
trials = 2

for(i in 1:nrow(df_agents)){ # iterate over agents
  for(t in 1:trials){ # iterate over trials
    df_sim <- rbind(df_sim, SocialConformityAgent(df_agents$AgentID[i], df_agents$bias[i], df_agents$socialConf[i]))
  }
}

```


```{r}
#for(i in length(df_agents)){
#  print(df_agents$AgentID)}

df_sim <- rbind(df_sim, SocialConformityAgent(df_agents$AgentID[3], df_agents$bias[3], df_agents$socialConf[3]))


for(i in 1:nrow(df_agents)){ # iterate over agents
  print(paste(df_agents$AgentID[i], df_agents$bias[i], df_agents$socialConf[i]))
  #df_sim <- rbind(df_sim, SocialConformityAgent(df_agents$AgentID[i], df_agents$bias[i], df_agents$socialConf[i]))
}

```

